### 2024-10-07 paper/main.tex
Initial commit

\documentclass[12pt]{article}

% Packages for formatting and math
\usepackage{amsmath, amsthm, amssymb}
\usepackage{cite}
\usepackage{geometry}
\geometry{a4paper, margin=2.5cm}

% Theorem and Proof setup
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

% Title Section
\title{MATD02 - Exploration of Finite Geometry }
\author{Your Name}
\date{}

\begin{document}

    \maketitle

    \begin{abstract}
        This is where you write a brief paragraph summarizing the main idea of your topic and your approach. Keep it concise and clear, offering a high-level view of your paper.
    \end{abstract}

    \section{Introduction}
    Begin your report by introducing the topic. Clearly define the key concepts, notations, and theorems that will be discussed. Keep the language accessible to the entire MATD02 class.

    \section{Theorems and Proofs}

    \begin{theorem}
        State the first theorem here.
    \end{theorem}

    \begin{proof}
        Provide the proof for Theorem 1 here, step by step.
    \end{proof}

    \begin{theorem}
        State the second theorem here.
    \end{theorem}

    \begin{proof}
        Provide the proof for Theorem 2 here, ensuring clarity and logical flow.
    \end{proof}

    \section{Future Developments}
    In this section, discuss any potential future developments related to your topic. Mention related problems, extensions, or more advanced ideas, even if their proofs are not currently clear.

    \section{Conclusion}
    Summarize the key points covered in the report, including the theorems and their significance. Restate the main takeaways in a clear, concise manner.

    % References
    \bibliography{references}
    \bibliographystyle{IEEEtran}
\end{document}

%\begin{document}
%    When you are not looking at it, this sentences stops citing~\cite{knuth1990}.
%
%    \bibliography{references}
%    \bibliographystyle{plain}
%\end{document}

### 2024-10-07 src/project.ts

@@ -1,0 +1,8 @@
+import {makeProject} from '@motion-canvas/core';
+import audio from '../audio/test.mp3';
+import example from './scenes/example?scene';
+import example2 from "./scenes/example2?scene";
+
+export default makeProject({
+  scenes: [example, example2],
+});

### 2024-10-20 paper/main.tex
chore: Get outline up for report, add some potential citations to look at fix: Revert scenes to an example to get them compiling

@@
     \begin{abstract}
-        This is where you write a brief paragraph summarizing the main idea of your topic and your approach. Keep it concise and clear, offering a high-level view of your paper.
+        Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+        Pellentesque pretium ut neque ac lacinia.
+        Aenean ultricies dapibus ultricies.
+        Nam tristique posuere quam, eget varius lorem posuere a.
+        Nam hendrerit magna ex, vehicula tempor quam maximus at.
+        Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+        Nullam vitae ultrices nulla, at dapibus lectus.
+        Nullam ultrices eros eu lorem laoreet elementum.
+        Nullam ullamcorper in lectus vel varius.
+        Praesent lobortis sem vitae elit posuere, in consectetur magna tempor.
+        Vivamus nunc ligula, ullamcorper ac sapien vel, dignissim varius leo.
+        Mauris vel suscipit metus, id ornare odio.
+        Vivamus ultricies vehicula mi ut bibendum.
+        Nullam sollicitudin elit sit amet velit lacinia, eget pretium nisl viverra.
+        Nulla laoreet nisi non velit posuere, a vehicula diam vehicula.
+        Donec fermentum commodo tortor, ac feugiat orci iaculis sit amet.
+        Suspendisse luctus, velit eu placerat dapibus, justo felis mattis tortor, vitae blandit leo justo vitae nibh.
     \end{abstract}
@@
     \section{Introduction}
-    Begin your report by introducing the topic. Clearly define the key concepts, notations, and theorems that will be discussed. Keep the language accessible to the entire MATD02 class.
 
-    \section{Theorems and Proofs}
+    Introduce four/five point geometries as a way to start thinking about geometries more abstractly, use notes from\cite{sinn_course_2021}
+
+    \section{The Fano plane}
 
     \begin{theorem}
-        State the first theorem here.
+        Ex. Each point is on exactly three lines
     \end{theorem}
@@
     \begin{proof}
-        Provide the proof for Theorem 1 here, step by step.
+
     \end{proof}
 
+    \section{Connections to finite groups}
+    Explore ideas in from the following sources\cite{carmichael_finite_1930,tsuzuku_finite_1982},
+    I'd really like to look at broader connections than symmetry groups.
+
     \begin{theorem}
-        State the second theorem here.
     \end{theorem}
@@
     \begin{proof}
-        Provide the proof for Theorem 2 here, ensuring clarity and logical flow.
     \end{proof}
@@
     \section{Future Developments}
-    In this section, discuss any potential future developments related to your topic. Mention related problems, extensions, or more advanced ideas, even if their proofs are not currently clear.
 
-    \section{Conclusion}
-    Summarize the key points covered in the report, including the theorems and their significance. Restate the main takeaways in a clear, concise manner.
+    Take a look at notes from the group theory textbooks.
 
@@
 \end{document}
-
-%\begin{document}
-%    When you are not looking at it, this sentences stops citing~\cite{knuth1990}.
-%
-%    \bibliography{references}
-%    \bibliographystyle{plain}
-%\end{document}

### 2024-11-11 paper/main.tex
chore: Work on getting outline for paper

@@
 \title{MATD02 - Exploration of Finite Geometry }
-\author{Your Name}
+\author{Danielle Voznyy}
 \date{}
@@
         Nullam ullamcorper in lectus vel varius.
-        Praesent lobortis sem vitae elit posuere, in consectetur magna tempor.
-        Vivamus nunc ligula, ullamcorper ac sapien vel, dignissim varius leo.
-        Mauris vel suscipit metus, id ornare odio.
-        Vivamus ultricies vehicula mi ut bibendum.
-        Nullam sollicitudin elit sit amet velit lacinia, eget pretium nisl viverra.
-        Nulla laoreet nisi non velit posuere, a vehicula diam vehicula.
-        Donec fermentum commodo tortor, ac feugiat orci iaculis sit amet.
-        Suspendisse luctus, velit eu placerat dapibus, justo felis mattis tortor, vitae blandit leo justo vitae nibh.
     \end{abstract}
@@
 
-    Introduce four/five point geometries as a way to start thinking about geometries more abstractly, use notes from\cite{sinn_course_2021}
+    Finite geometries are axiomatically defined finite sets of point and lines.
+    Set theory helps us provide a more rigorous definition of these elements,
+    we'll use the following simple definitions going forward:
 
-    \section{The Fano plane}
+    \begin{itemize}
+        \setlength\itemsep{0em}
+        \item Points are elements in a finite set \( S \).
+        \item Lines are elements in a subset of the power set of \( S \).
+        \item We say a point \( p \) is on a line \( l \) when \( p \in l \).
+        \item Lines \( l_1 \) and \( l_2 \) intersect when \( l_1 \cap l_2 \neq \emptyset \)..
+    \end{itemize}
+
+    Let's explore what axioms could lead to such a geometry.
+
+    \section{Finite planes}
+
+    \subsection{Finite affine planes}
+
+    \subsection{Finite projective planes}
+
+    Study fano plane
 
@@
 
-    \section{Connections to finite groups}
-    Explore ideas in from the following sources\cite{carmichael_finite_1930,tsuzuku_finite_1982},
-    I'd really like to look at broader connections than symmetry groups.
+    \subsection{Order of finite planes}
+
+    \section{Synthetic geometry and higher dimensions}
+
+    Notice we didn't have to talk about our points as being two-dimensional,
+    however something about the axioms we used let us represent our spaces as two dimensional planes.
+
+    Synthetic geometry studies such axiomatically defined geometries, and gives us tools to talk about
+    higher dimensional spaces with set theoretic definitions of dimension.
+
+    DEFINE projective plane axiomatically
+
+    DEFINE geometric dimension
+
+    \subsection{Projective spaces and geometric dimension}
+
+    Projective planes are two-dimensional projective spaces
 
@@
 
+    \subsection{Finite projective planes of order $\geq 3$ }
+
     \section{Future Developments}
@@
     Take a look at notes from the group theory textbooks.
+
+    \subsection{Conjectures}
+
+    From wiki: Is the order of a finite plane always a prime power?
 

### 2024-11-12 paper/main.tex
Add some definition references for finite projective geometry

@@
 \usepackage{geometry}
+\usepackage{csquotes}
 \geometry{a4paper, margin=2.5cm}
+
+%\setlength{\parskip}{\baselineskip}%
+%\setlength{\parindent}{0pt}
+\usepackage{parskip}
+\setlength{\parindent}{0pt}
 
@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{definition}{Definition}
 
@@
 
-    \section{Synthetic geometry and higher dimensions}
+    \section{Finite geometries in higher dimensions}
+
+%    Synthetic geometry studies such axiomatically defined geometries, and gives us tools to talk about
+%    higher dimensional spaces with set theoretic definitions of dimension.
 
     Notice we didn't have to talk about our points as being two-dimensional,
-    however something about the axioms we used let us represent our spaces as two dimensional planes.
+    however something about our choice of points let us represent our spaces as two-dimensional planes.
 
-    Synthetic geometry studies such axiomatically defined geometries, and gives us tools to talk about
-    higher dimensional spaces with set theoretic definitions of dimension.
+    In fact, when looking at projective geometry through the lens of infinite sets like $R$,
+    we get a definition of \enquote{projective spaces} by looking at one-dimensional vector subspaces of a vector space like $R^n$.\cite{weisstein_projective_nodate}
+%    The projective part of projective geometry can be thought of as adding points at infinity to such a vector space,
+    Here, our dimension comes from a concept of coordinates in the underlying vector space.
 
-    DEFINE projective plane axiomatically
+    In the finite case however\textemdash especially working purely from axioms\textemdash we don't have such an obvious idea of dimension.
+    We can, however, generalize concepts from vector spaces to get the following definitions.\cite{noauthor_projective_2024,beutelspacher_projective_2000}
 
-    DEFINE geometric dimension
+%    A subspace of the projective space is a subset X, such that any line containing two points of X is a subset of X (that is, completely contained in X).
+The full space and the empty space are always subspaces.
+    \begin{definition}
+        A subspace of the projective space is a subset X, such that any line containing two points of X is a subset of X (that is, completely contained in X).
+The full space and the empty space are always subspaces.
+    \end{definition}
 
-    \subsection{Projective spaces and geometric dimension}
-
-    Projective planes are two-dimensional projective spaces
+    \begin{definition}
+        The geometric dimension of the space $P$ is said to be n if that is the largest number for which there is a strictly ascending chain of subspaces of this form:
+        \[\emptyset = X_{-1}\subset X_{0}\subset \cdots X_{n}=P.\]
+    \end{definition}
 
     \begin{theorem}
+        Projective planes are projective spaces of dimension 2.
     \end{theorem}
@@
 
-    \subsection{Finite projective planes of order $\geq 3$ }
+    \subsection{Finite projective spaces of dimension $\geq 3$ }
 
     \section{Future Developments}
-
-    Take a look at notes from the group theory textbooks.
 

### 2024-11-12 paper/main.tex
Get most of the introduction finished

@@
 \usepackage{parskip}
+\usepackage{amssymb}
+\usepackage{amsfonts}
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
 \setlength{\parindent}{0pt}
@@
     \begin{abstract}
-        Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-        Pellentesque pretium ut neque ac lacinia.
-        Aenean ultricies dapibus ultricies.
-        Nam tristique posuere quam, eget varius lorem posuere a.
-        Nam hendrerit magna ex, vehicula tempor quam maximus at.
-        Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-        Nullam vitae ultrices nulla, at dapibus lectus.
-        Nullam ultrices eros eu lorem laoreet elementum.
-        Nullam ullamcorper in lectus vel varius.
+        We explore finite geometries through a synthetic point of view.
+        Starting with axioms, we explore finite planes, their orders, and prove some properties about the Fano plane.
+        We then look at how concepts like dimension in projective spaces can be described without coordinate systems.
+        Finally, we discuss some conjectures and future directions in the field.
     \end{abstract}
 
-    \section{Introduction}
+    \section{Finite plane geometry}
 
-    Finite geometries are axiomatically defined finite sets of point and lines.
-    Set theory helps us provide a more rigorous definition of these elements,
-    we'll use the following simple definitions going forward:
+    Finite geometries provide a good introduction to axiomatic, sometimes called synthetic, definitions of geometries
+    because they work with finite number of points that can help visualize more abstract concepts.
 
-    \begin{itemize}
-        \setlength\itemsep{0em}
-        \item Points are elements in a finite set \( S \).
-        \item Lines are elements in a subset of the power set of \( S \).
-        \item We say a point \( p \) is on a line \( l \) when \( p \in l \).
-        \item Lines \( l_1 \) and \( l_2 \) intersect when \( l_1 \cap l_2 \neq \emptyset \)..
-    \end{itemize}
+    We'll begin by describing finite planes using two sets and the set containment relation.
 
-    Let's explore what axioms could lead to such a geometry.
+    \begin{definition}
+        Let $P$ be nonempty a finite set and $L \subseteq \mathcal{P}(P)$, be a nonempty subset of the power set of $P$.
 
-    \section{Finite planes}
+        We'll call an element of $P$ is a point in our space, and an element of $L$ is a line.
+        We say a point $p$ is on a line when $p \in L$ and lines $L_1, L_2$ intersect when $L_1 \cap L_2 \neq \emptyset$
+        \todo{Mention that there's more abstract definitions? We like to talk about planes and more in higher dimensions but unsure if relevant to this.}
+        .
+    \end{definition}
 
-    \subsection{Finite affine planes}
+    We can now categorize these planes using axioms.
+    Two broad types of geometries come from a similar set of axioms which differ in the existence of parallel lines.
+    Affine geometry, where parallel lines exist, and projective geometry, where they do not.
+    As it turns out, these are quite similar despite projective geometry being simpler to work with\cite[p.~7]{beutelspacher_projective_2000}.
 
@@
 
-    Study fano plane
+    Let's begin by defining projective spaces axiomatically, with an extra axiom for projective planes,
+
+    \begin{definition}
+        A projective space is a such that,
+        \begin{itemize}
+            \item For distinct points $p, q$, there is exactly one line $L$ such that ${p,q} \subseteq L$.
+            We call it the line containing $p, q$, or just the line $pq$.
+            \item Given points $a,b,c,d$, if $ab$ intersects $cd$, then $ac$ intersects $bd$
+            \item Any line contains at least three elements.
+            \item We call this projective space a projective plane if any two lines intersect.
+        \end{itemize}
+    \end{definition}
+
+    \subsubsection{The fano plane}
+
+    Study fano plane\todo[inline]{Not sure what the best way to introduce this is? Space for a quick proof about it containing 7 points, an image?}
+
+    \subsection{Order of finite projective spaces}
+
+    Finite projective spaces have an interesting property, all their lines contain an equal number of elements, which gives rise to an idea of order.
 
     \begin{theorem}
-        Ex. Each point is on exactly three lines
+        Given a projective space, there exists a positive integer $q$ such that any line in $L$ contains exactly $q+1$ elements.
+        We call q the order of this space.
     \end{theorem}
@@
     \begin{proof}
-
+        \todo[inline]{Prove.}
     \end{proof}
 
-    \subsection{Order of finite planes}
-
-    \section{Finite geometries in higher dimensions}
+    \section{Dimension in finite projective spaces}
 
@@
 
-    Notice we didn't have to talk about our points as being two-dimensional,
-    however something about our choice of points let us represent our spaces as two-dimensional planes.
+    Notice to give our projective space an idea of being planes (somehow being two-dimensional), we had to add an axiom stating any two lines intersect.
+    We might now wonder what this axiom actually does, and what the idea of dimension even means here.
 
-    In fact, when looking at projective geometry through the lens of infinite sets like $R$,
-    we get a definition of \enquote{projective spaces} by looking at one-dimensional vector subspaces of a vector space like $R^n$.\cite{weisstein_projective_nodate}
+    In fact, when looking at projective geometry through the lens of infinite sets like $\mathbb{R}$,
+    we get a definition of projective spaces by looking at one-dimensional vector subspaces of a vector space like $\mathbb{R}^n$.\cite{weisstein_projective_nodate}
 %    The projective part of projective geometry can be thought of as adding points at infinity to such a vector space,
@@
 
-    In the finite case however\textemdash especially working purely from axioms\textemdash we don't have such an obvious idea of dimension.
+    In the finite case\textemdash especially working purely from axioms\textemdash we don't have such an obvious idea of dimension.
     We can, however, generalize concepts from vector spaces to get the following definitions.\cite{noauthor_projective_2024,beutelspacher_projective_2000}
 
-%    A subspace of the projective space is a subset X, such that any line containing two points of X is a subset of X (that is, completely contained in X).
-The full space and the empty space are always subspaces.
     \begin{definition}
@@
     \begin{proof}
+        \todo[inline]{Prove.}
     \end{proof}
+
+    \todo[inline]{I believe this definition can be described more intuitively as being able to draw continuous versions of our lines through points in n-dimensions without the lines intersecting.}
 
@@
 
+    As it turns out, order and dimension are powerful tools for classifying finite geometries.
+    In fact, we use the notation $PG(n, q)$ to talk about projective spaces of dimension $n$ and order $q+1$
+    that arise from a field of order $q$, written $GF(q)$ (since they are isomorphic up to order.)\todo{Quickly mention what isomorphism means for projective spaces.}
+
+    The Veblen-Young theorem shows finite projective spaces of dimension $n \geq 3$ can always be described using such a field, up to isomorphism.
+    However, finite projective planes can be constructed in more ways, specifically non-Desarguesian planes, which make
+    it much harder to classify planes of order two\todo{Mention examples? State Desargues' theorem?}.
+
     \section{Future Developments}
 
-    \subsection{Conjectures}
+    The difficulty in classifying finite projective planes gives rise to an open question:
 
-    From wiki: Is the order of a finite plane always a prime power?
+    \textit{Is the order of a finite plane always a prime power?}
+
+    \todo[inline]{Bruck–Ryser theorem}
+    \todo[inline]{Classification up to order 10, why is it so difficulty to do past this small number?}
 

### 2024-11-14 paper/main.tex
Start both proofs, incorporate ideas further into paper Work on future developments section

--- 2024-11-11 paper/main.tex
@@
 \usepackage{geometry}
+\usepackage{csquotes}
 \geometry{a4paper, margin=2.5cm}
+
+%\setlength{\parskip}{\baselineskip}%
+%\setlength{\parindent}{0pt}
+\usepackage{parskip}
+\usepackage{amssymb}
+\usepackage{tikz}
+\usepackage{amsfonts}
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
+\usepackage{biblatex}
 
@@
     \begin{abstract}
-        Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-        Pellentesque pretium ut neque ac lacinia.
-        Aenean ultricies dapibus ultricies.
-        Nam tristique posuere quam, eget varius lorem posuere a.
-        Nam hendrerit magna ex, vehicula tempor quam maximus at.
-        Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-        Nullam vitae ultrices nulla, at dapibus lectus.
-        Nullam ultrices eros eu lorem laoreet elementum.
-        Nullam ullamcorper in lectus vel varius.
+        We explore finite geometries through a synthetic point of view.
+        Starting with axioms, we define finite projective spaces and planes.
+        We discuss the concepts of order and dimension in these spaces,
+        specifically how dimension in projective spaces can be described without a coordinate system.
+        Finally, we discuss an open conjecture about the order of finite planes.
     \end{abstract}
@@
 
-    Finite geometries are axiomatically defined finite sets of point and lines.
-    Set theory helps us provide a more rigorous definition of these elements,
-    we'll use the following simple definitions going forward:
+    Finite geometries provide a good introduction to axiomatic, sometimes called synthetic, definitions of geometries
+    because they work with finite number of points that can help visualize more abstract concepts.
+    \todo{Look over intro again, finite is nice for abstract sets I guess.}
 
-    \begin{itemize}
-        \setlength\itemsep{0em}
-        \item Points are elements in a finite set \( S \).
-        \item Lines are elements in a subset of the power set of \( S \).
-        \item We say a point \( p \) is on a line \( l \) when \( p \in l \).
-        \item Lines \( l_1 \) and \( l_2 \) intersect when \( l_1 \cap l_2 \neq \emptyset \)..
-    \end{itemize}
+    We'll begin by describing finite geometries using two sets and the set containment relation
+    (noting these definitions often differ based on the context.)
 
-    Let's explore what axioms could lead to such a geometry.
+    \begin{definition}
+        Let $P$ be nonempty a finite set and $\mathcal{L} \subseteq \mathcal{P}(P)$, be a nonempty subset of the power set of $P$,
+        then $(P, \mathcal{L})$ is a geometry.
 
-    \section{Finite planes}
+        We'll call an element of $P$ a point in our space, and an element of $\mathcal{L}$ a line.
+        We say a point $p$ is on a line $L$ when $p \in L$ and lines $L_1, L_2$ intersect when $L_1 \cap L_2 \neq \emptyset$.
+    \end{definition}
 
-    \subsection{Finite affine planes}
+    We can now categorize these spaces using axioms, starting with planes.
+    Two broad types of plane geometries come from a similar set of axioms which differ in the existence of parallel lines.
+    Affine geometry, where parallel lines exist, and projective geometry, where they do not.
+    As it turns out, these are quite similar despite projective geometry being simpler to work with\cite[p.~7]{beutelspacher_projective_2000}.
 
@@
 
-    Study fano plane
+    Let's begin by defining projective spaces axiomatically, with an extra axiom for projective planes,
+
+    \begin{definition}
+        A projective space is a geometry such that,
+        \begin{itemize}
+            \item A1 - For distinct points $p, q$, there is exactly one line $L$ such that $\{p,q\} \subseteq L$.
+            We call it the line containing $p, q$, or just the line $pq$.
+            \item A2 - Given points $a,b,c,d$, if $ab$ intersects $cd$, then $ac$ intersects $bd$
+            \item A3 - Any line contains at least 3 elements.
+            \item A4 - We call this projective space a projective plane if any two lines have at least one point in common, i.e. they intersect
+        \end{itemize}
+    \end{definition}
+
+    To avoid simple cases, we often also assume that the space has at least two lines.
+    The Fano plane is an example of such a projective plane, in fact it is the smallest projective plane,
+    containing 7 points and 7 lines, illustrated below:
+
+%   From: https://tex.stackexchange.com/questions/208894/how-might-i-typeset-the-fano-plane-in-latex
+    \begin{figure}[h]
+        \centering
+        \label{fig:fano_plane}
+        \tikz[every node/.style={circle, fill, scale=0.5}]
+        \draw circle [radius=1] (90:2) -- (210:2) -- (330:2) -- cycle (0,0) node {}
+        \foreach \i in {90,210,330}{ (\i:2) node {} -- (\i+180:1) node {} };
+    \end{figure}
+
+    It's fairly routine work to show the set of points and lines shown above do in fact satisfy our earlier axioms,
+    however more interesting is that this plane has the same number of points and all lines contain three points.
+    Does this generalize to all projective spaces?
+
+    \section{Order of finite projective spaces}
+
+    In fact, these do generalize, we call the first concept duality,
+    in which theorems about lines on a projective plane also have duals regarding points (and vice-versa).
+    This generalizes further to higher dimensions with dual spaces.
+    The second only makes sense in the finite case, and gives rise to a concept of order. \cite[p. 24]{beutelspacher_projective_2000}
 
     \begin{theorem}
-        Ex. Each point is on exactly three lines
+        Given a finite projective space, there exists a positive integer $q$ such that any line in $L$ contains exactly $q+1$ elements.
+        We call q the order of this space.
     \end{theorem}
@@
     \begin{proof}
+        Given any two lines $L_1, L_2$, we'll argue there exists a bijection $\phi: L_1 \rightarrow L_2$,
+        and thus all lines have the same number of elements.
+        If $L_1 = L_2$ we are done, so we consider distinct lines.
 
+        Case: $L_1$ intersects $L_2$
+
+        Then $\{a, b\} \subseteq L_1$ and $\{a, c\} \subseteq L_2$ for some points $a,b,c$,
+        since by A3 both lines contain at least 3 distinct points and by supposition we have at least one shared point.
+
+        As well, by A3 line $bc$ must contain another point, name it $p$, moreover $p \notin L_1, L_2$,
+        otherwise $L_1 = L_2$ by A1, the uniqueness of lines through points.
+
+        Then given any other point $x \in L_1$, consider the line $xp$.
+        We'll show this must intersect $L_2$ using A2 and call the intersection point $\phi(x)$.
+
+        \begin{figure}[h]
+            \centering
+            \begin{tikzpicture}
+                % Draw the lines
+                \draw[thick] (-2,0) -- (3,1) node[right] {$L_1$};
+                \draw[thick] (-2,0) -- (3,-1) node[right] {$L_2$};
+                % Draw the intersection point
+                \fill (-2,0) circle (2pt) node[below] {$a$};
+                % Label points on L1
+                \fill (2,0.8) circle (2pt) node[above] {$b$};
+                \fill (0,0.4) circle (2pt) node[above] {$x$};
+                % Label points on L2
+                \fill (2,-0.8) circle (2pt) node[below] {$\phi(x)$};
+                \fill (0,-0.4) circle (2pt) node[below] {$c$};
+                % Draw intersecting lines
+                \draw[thick] (2,-0.8) -- (0,0.4)
+                \draw[thick] (2,0.8) -- (0,-0.4)
+                \fill (0.7,0) circle (2pt) node[below] {$p$};
+            \end{tikzpicture}
+%            \caption{Illustration of our points and lines}
+            \label{fig:intersecting_lines}
+        \end{figure}
+
+        Given points $a,b,c,d$, if $ab$ intersects $cd$, then $ac$ intersects $bd$
+        Given points $a,b,c,d$, if $ab$ intersects $cd$, then $ac$ intersects $bd$
     \end{proof}
 
-    \subsection{Order of finite planes}
+    \section{Dimension of finite projective spaces}
 
-    \section{Synthetic geometry and higher dimensions}
+    The use of the term plane for our extra axiom\textemdash stating any two lines must intersect\textemdash seems connected to a two-dimensional space.
+    We might now wonder what this axiom actually does, and what the idea of dimension even means for the abstract sets we used.
 
-    Notice we didn't have to talk about our points as being two-dimensional,
-    however something about the axioms we used let us represent our spaces as two dimensional planes.
+    In fact, when looking at projective geometry through the lens of infinite fields like $\mathbb{R}$,
+    we get a definition of projective spaces by looking at one-dimensional vector subspaces of a vector space like $\mathbb{R}^n$.\cite{weisstein_projective_nodate}
+    Here, our dimension comes from a concept of coordinates in the underlying vector space, i.e.\ its basis.
 
-    Synthetic geometry studies such axiomatically defined geometries, and gives us tools to talk about
-    higher dimensional spaces with set theoretic definitions of dimension.
+    In the finite case\textemdash especially working purely from axioms\textemdash
+    we don't have such an obvious idea of dimension.
+    We can, however, generalize concepts from vector spaces to get the following definitions.\cite{noauthor_projective_2024,beutelspacher_projective_2000}
 
-    DEFINE projective plane axiomatically
+    \begin{definition}
+        A subspace of the projective space is a subset $X \subseteq P$,
+        such that any line containing two points of X is a subset of X (that is, completely contained in X).
+        The full space and the empty space are always subspaces.
+    \end{definition}
 
-    DEFINE geometric dimension
-
-    \subsection{Projective spaces and geometric dimension}
-
-    Projective planes are two-dimensional projective spaces
+    \begin{definition}
+        The geometric dimension of the space $P$ is said to be n if that is the largest number for which there is a strictly ascending chain of subspaces of this form:
+        $\emptyset = X_{-1}\subset X_{0}\subset \cdots X_{n}=P.$
+    \end{definition}
 
     \begin{theorem}
+        Projective planes are projective spaces of dimension 2.
     \end{theorem}
@@
     \begin{proof}
+        By A4, any two lines $L_1, L_2$ intersect.
+        Thus, any nonempty subspace $X$ containing a line $L$
+        \todo{Prove.}
     \end{proof}
 
-    \subsection{Finite projective planes of order $\geq 3$ }
+    This proof highlights the idea behind this geometric dimension definition,
+    our chain of subspaces is akin to talking about different objects of increasing dimension in our space.
+    That is, points in lines, lines in planes,\ldots, up to $n-1$ dimensional hyperplanes, to the full space itself.
+
+    \subsection{Finite projective spaces of dimension $\geq 3$ }
+
+    As it turns out, order and dimension are powerful tools for classifying finite geometries.
+    In fact, we use the notation $PG(n, q)$ to talk about finite projective spaces of dimension $n$ and order $q+1$
+    that arise from a finite field of order $q$, written $GF(q)$ (since they are isomorphic up to order.)\todo{Quickly mention what isomorphism means for projective spaces.}
+
+    The Veblen-Young theorem shows finite projective spaces of dimension $n \geq 3$ can always be described using such a field.
+    Finite projective planes are much harder to classify, since they can be constructed in more ways.
+    Specifically, non-Desarguesian planes.
+
+    \todo{Mention examples? State Desargues' theorem?}
 
@@
 
-    Take a look at notes from the group theory textbooks.
+    The difficulty in classifying finite projective planes gives rise to an open question:
 
-    \subsection{Conjectures}
+    \textit{Is the order of a finite projective plane always a prime power?}
 
-    From wiki: Is the order of a finite plane always a prime power?
+    The number of non-isomorphic planes are known up to order 10: $1, 1, 1, 1, 0, 1, 1, 4, 0$.
+    Moreover, the Bruck-Ryser theorem states for $n \equiv 1,2\ (mod\ 4)$ and $n$ is not the sum of two squares,
+    then no plane exists of order $n$.\cite{https://oeis.org/A001231}
+    \todo{Insert citation into bibtex}
+
+    \todo{Bruck–Ryser theorem}
+    \todo{Classification up to order 10, why is it so difficulty to do past this small number?}
 

### 2024-11-15 paper/main.tex
Finish proof for theorem 2

@@
 \usepackage{amsfonts}
+\usepackage{enumitem}
 \usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
-\usepackage{biblatex}
+\usepackage{wrapfig}
 
@@
     \todo{Look over intro again, finite is nice for abstract sets I guess.}
-
-    We'll begin by describing finite geometries using two sets and the set containment relation
-    (noting these definitions often differ based on the context.)
+    We'll begin by describing finite geometries using two sets and the set containment relation.\footnote{
+        Both the definition for geometries and projective spaces are modified from \cite[p.~1,7]{beutelspacher_projective_2000},
+        which uses an arbitrary symmetric and reflexive relation.
+        We opt for set containment for its familiarity.}
 
@@
     Affine geometry, where parallel lines exist, and projective geometry, where they do not.
-    As it turns out, these are quite similar despite projective geometry being simpler to work with\cite[p.~7]{beutelspacher_projective_2000}.
+    As it turns out, these are quite similar despite projective geometry being simpler to work with.
 
-    \subsection{Finite projective planes}
-
-    Let's begin by defining projective spaces axiomatically, with an extra axiom for projective planes,
+    We start by defining projective spaces and planes axiomatically:
 
@@
         A projective space is a geometry such that,
-        \begin{itemize}
+        \begin{itemize}[noitemsep]
             \item A1 - For distinct points $p, q$, there is exactly one line $L$ such that $\{p,q\} \subseteq L$.
             We call it the line containing $p, q$, or just the line $pq$.
-            \item A2 - Given points $a,b,c,d$, if $ab$ intersects $cd$, then $ac$ intersects $bd$
+            \item A2 - Given distinct points $a,b,c,d$, if $ab$ intersects $cd$, then $ac$ intersects $bd$
             \item A3 - Any line contains at least 3 elements.
             \item A4 - We call this projective space a projective plane if any two lines have at least one point in common, i.e. they intersect
+            \item S1 - To avoid simple cases, we add that at least two lines and points exist.
         \end{itemize}
@@
 
-    To avoid simple cases, we often also assume that the space has at least two lines.
-    The Fano plane is an example of such a projective plane, in fact it is the smallest projective plane,
-    containing 7 points and 7 lines, illustrated below:
-
 %   From: https://tex.stackexchange.com/questions/208894/how-might-i-typeset-the-fano-plane-in-latex
-    \begin{figure}[h]
+%    \begin{figure}[h]
+    \begin{wrapfigure}{r}{0.25\textwidth}
         \centering
@@
         \foreach \i in {90,210,330}{ (\i:2) node {} -- (\i+180:1) node {} };
-    \end{figure}
+    \end{wrapfigure}
 
-    It's fairly routine work to show the set of points and lines shown above do in fact satisfy our earlier axioms,
+    The Fano plane, shown to the right, is an example of such a projective plane,
+    in fact it is the smallest projective plane, containing 7 points and 7 lines.
+
+    It's fairly routine work to show the set of points and lines shown do in fact satisfy our earlier axioms,
     however more interesting is that this plane has the same number of points and all lines contain three points.
@@
     This generalizes further to higher dimensions with dual spaces.
-    The second only makes sense in the finite case, and gives rise to a concept of order. \cite[p. 24]{beutelspacher_projective_2000}
+    The second gives rise to a concept of order\cite[p. 24]{beutelspacher_projective_2000}.
 
     \begin{theorem}
-        Given a finite projective space, there exists a positive integer $q$ such that any line in $L$ contains exactly $q+1$ elements.
+        Given a projective space, there exists a positive integer $q$ such that any line in $L$ contains exactly $q+1$ elements.
         We call q the order of this space.
@@
 
-        Case: $L_1$ intersects $L_2$
+        \underline{Case 1}: $L_1$ intersects $L_2$
 
@@
         Given points $a,b,c,d$, if $ab$ intersects $cd$, then $ac$ intersects $bd$
-        Given points $a,b,c,d$, if $ab$ intersects $cd$, then $ac$ intersects $bd$
+
+        \underline{Case 2}: $L_1$ does not intersect $L_2$
     \end{proof}
@@
     In fact, when looking at projective geometry through the lens of infinite fields like $\mathbb{R}$,
-    we get a definition of projective spaces by looking at one-dimensional vector subspaces of a vector space like $\mathbb{R}^n$.\cite{weisstein_projective_nodate}
+    we get a definition of projective spaces by looking at one-dimensional vector subspaces of a vector space like $\mathbb{R}^n$ \cite{weisstein_projective_nodate}.
     Here, our dimension comes from a concept of coordinates in the underlying vector space, i.e.\ its basis.
 
-    In the finite case\textemdash especially working purely from axioms\textemdash
-    we don't have such an obvious idea of dimension.
-    We can, however, generalize concepts from vector spaces to get the following definitions.\cite{noauthor_projective_2024,beutelspacher_projective_2000}
+    Working purely from axioms we don't have such an obvious idea of dimension.
+    We can, however, generalize concepts from vector spaces to get the following definitions.\footnote{
+        The two definitions come from Wikipedia \cite{noauthor_projective_2024},
+        I could not find a text referencing them exactly, my assumption is something cited nearby states them in a modified form.
+        Nevertheless, I found them fascinating as a demonstration of dimension in an abstract context.
+    }
 
@@
     \begin{proof}
-        By A4, any two lines $L_1, L_2$ intersect.
-        Thus, any nonempty subspace $X$ containing a line $L$
-        \todo{Prove.}
+        Let $P$ be the set of points in our plane, noting $|P|\geq 2$ by S1.
+
+        \underline{Part 1}: \textit{The dimension of our plane must be at least 2.}
+
+        Consider any point $a \in P$, $\{ a \}$ is a subspace of $P$ vacuously since it doesn't contain two points.
+        Now, given any other point $b$, $ab$ is the only line that passes through two points of $ab$ by A1.
+        So $ab$ is a subspace since $ab \subseteq ab$.
+        Finally, $P$ has at least two lines by S1, so $ab \subset P$.
+        So we have a chain of subspaces $\emptyset \subset \{a\} \subset ab \subset P$, thus our geometric dimension is at least 2.
+
+        \underline{Part 2}: \textit{The dimension of our plane must be at most 2.}
+
+        In a maximal chain of subspaces, any subspace $X_i$ must have that there does not exist a subspace $X$ for which $X_{i-1} \subset X \subset X_i$.
+        Since any nonempty subspace $X$ must contain a point $a$ and $\{a\}$ is a subspace (as shown earlier),
+        with no sets existing between $\emptyset$ and $\{a\}$, we must have in our chain that $X_0 = \{a\}$.
+
+        Similarly, since $X_0 \subset X_1$, $X_1$ contains at least another point $b$, and again the line $ab$ is a subspace as shown earlier.
+        Any strict subset of $ab \neq \emptyset, \{a\}$ would not contain the line $ab$ in full and thus cannot be a subspace.
+        So it must be that $X_1 = ab$.
+
+        Now, since $X_1 \subset X_2$, we must have a distinct $c \in X_2$ such that $c \notin X_2 = ab$.
+        So we have three distinct points $a,b,c$ which form three distinct lines by our choice of $c$.
+        We'll show any other line in our space must also be in $X_2$.
+        Let $x,y \in P$ be arbitrary points, wlog we can say $y \in ab$ since by A4, $xy$ must intersect $ab$ at some point.
+        Again by A4, let $xy$ intersect $bc$ at $z_1$, and $ac$ at $z_2$.
+
+        \begin{figure}[h]
+            \label{fig:triangle}
+            \centering
+            \begin{tikzpicture}
+                % Draw the lines
+                \draw[thick] (-1,0) -- (0,1.732);% node[right] {$L_1$};
+                \draw[thick] (1,0) -- (0,1.732);% node[right] {$L_2$};
+                \draw[thick] (-1,0) -- (1,0);
+                % Draw the intersection point
+                \fill (-1,0) circle (2pt) node[below] {$a$};
+                \fill (0,1.732) circle (2pt) node[above] {$b$};
+                \fill (1,0) circle (2pt) node[below] {$c$};
+
+                \fill (-1.5,1.3) circle (2pt) node[above] {$x$};
+                \fill (-0.5,0.85) circle (2pt) node[below] {$y$};
+                \fill (0.86346, 0.23644) circle (2pt) node[right] {$z$};
+                \draw[thick] (-1.5,1.3) -- (0.86346, 0.23644);
+            \end{tikzpicture}
+            \caption{Intuitively, regardless of our choice of $x$, since $xy$ also intersects $bc$, and $ac$, we'll have a distinct point $z$ on one of the two lines.}
+        \end{figure}
+
+        Suppose $y = z_1 = z_2$, then we have that all three lines $ab,bc,ac$ share one point $y$,
+        but then $\{b, y\} \subseteq ab$ and $\{b, y\} \subseteq bc$, so $ab = by = bc$ by A1,
+        since $by$ is the unique line passing through $b, y$.
+        But this contradicts $ab, bc$ being distinct lines.
+        Thus, we must have that $y \neq z$ where $z$ is one of $z_1$ or $z_2$.
+
+        Finally, the line $xy$ contains points $y,z \in X_2$, and since $X_2$ is a subspace we must have that $xy \in X_2$
+        So, $X_2$ = $P$ since any two points in $P$ form a line (containing them) that is fully contained in $X_2$.
+        Thus, the dimension is at most 2.
     \end{proof}
@@
     our chain of subspaces is akin to talking about different objects of increasing dimension in our space.
-    That is, points in lines, lines in planes,\ldots, up to $n-1$ dimensional hyperplanes, to the full space itself.
+    That is, points in lines, lines in planes \ldots up to $n-1$ dimensional hyperplanes, to the full space itself.
 
-    \subsection{Finite projective spaces of dimension $\geq 3$ }
+    \section{Future Developments}
 
@@
     In fact, we use the notation $PG(n, q)$ to talk about finite projective spaces of dimension $n$ and order $q+1$
-    that arise from a finite field of order $q$, written $GF(q)$ (since they are isomorphic up to order.)\todo{Quickly mention what isomorphism means for projective spaces.}
+    that arise from a finite field of order $q$, written $GF(q)$ (since they are isomorphic up to order.)\cite[p.~xv]{hirschfeld_general_2016}
 
     The Veblen-Young theorem shows finite projective spaces of dimension $n \geq 3$ can always be described using such a field.
-    Finite projective planes are much harder to classify, since they can be constructed in more ways.
+    However, finite projective planes are much harder to classify, since they can be constructed in more ways.
     Specifically, non-Desarguesian planes.
-
+    The difficulty in classifying finite projective planes gives rise to an open question:
+    \textit{Is the order of a finite projective plane always a prime power?}
     \todo{Mention examples? State Desargues' theorem?}
 
-    \section{Future Developments}
-
-    The difficulty in classifying finite projective planes gives rise to an open question:
-
-    \textit{Is the order of a finite projective plane always a prime power?}
-
-    The number of non-isomorphic planes are known up to order 10: $1, 1, 1, 1, 0, 1, 1, 4, 0$.
-    Moreover, the Bruck-Ryser theorem states for $n \equiv 1,2\ (mod\ 4)$ and $n$ is not the sum of two squares,
-    then no plane exists of order $n$.\cite{https://oeis.org/A001231}
-    \todo{Insert citation into bibtex}
+    The number of non-isomorphic finite projective planes is only known up to order 10: $1, 1, 1, 1, 0, 1, 1, 4, 0$
+    due to the computational complexity of verifying this using brute force\cite{lam_computer_1991,lam_non-existence_1989}.
+    Moreover, the closest we have come to a proof of this conjecture is the Bruck-Ryser theorem, which states if $n \equiv 1,2\ (mod\ 4)$ and $n$ is not the sum of two squares,
+    then no plane exists of order $n$.
 
@@
     % References
+    \newpage
     \bibliography{references}

### 2024-11-15 paper/main.tex
Some cleanup and fix citation urls

@@
 
-%\setlength{\parskip}{\baselineskip}%
-%\setlength{\parindent}{0pt}
 \usepackage{parskip}
@@
 \usepackage{wrapfig}
+
+% Format bibliography links correctly
+\usepackage[hidelinks]{hyperref}
+\usepackage[T1]{fontenc}
 
@@
 
-    Finite geometries provide a good introduction to axiomatic, sometimes called synthetic, definitions of geometries
-    because they work with finite number of points that can help visualize more abstract concepts.
-    \todo{Look over intro again, finite is nice for abstract sets I guess.}
+    Finite geometries provide a good starting point to axiomatic, sometimes called synthetic, definitions of geometries.
+    We can visualize finite geometries with as little as 7 points and lines and use them to explore abstract concepts.
     We'll begin by describing finite geometries using two sets and the set containment relation.\footnote{
-        Both the definition for geometries and projective spaces are modified from \cite[p.~1,7]{beutelspacher_projective_2000},
+        Both the definition for geometries and projective spaces are modified from \cite[p.~1,7]{beutelspacher_projective_1998},
         which uses an arbitrary symmetric and reflexive relation.
@@
         Let $P$ be nonempty a finite set and $\mathcal{L} \subseteq \mathcal{P}(P)$, be a nonempty subset of the power set of $P$,
-        then $(P, \mathcal{L})$ is a geometry.
+        then $(P, \mathcal{L})$ is finite a geometry.
 
-        We'll call an element of $P$ a point in our space, and an element of $\mathcal{L}$ a line.
+        We call an element of $P$ a point in our space, and an element of $\mathcal{L}$ a line.
         We say a point $p$ is on a line $L$ when $p \in L$ and lines $L_1, L_2$ intersect when $L_1 \cap L_2 \neq \emptyset$.
@@
             \item A4 - We call this projective space a projective plane if any two lines have at least one point in common, i.e. they intersect
-            \item S1 - To avoid simple cases, we add that at least two lines and points exist.
+            \item S1 - To avoid simple cases, we add that at least two lines (and thus points) exist.
         \end{itemize}
@@
 
-    In fact, these do generalize, we call the first concept duality,
+    In fact, it does generalize, we call the first concept duality,
     in which theorems about lines on a projective plane also have duals regarding points (and vice-versa).
-    This generalizes further to higher dimensions with dual spaces.
-    The second gives rise to a concept of order\cite[p. 24]{beutelspacher_projective_2000}.
+    The second gives rise to a concept of order\cite[p. 24]{beutelspacher_projective_1998}.
 
@@
     In fact, when looking at projective geometry through the lens of infinite fields like $\mathbb{R}$,
-    we get a definition of projective spaces by looking at one-dimensional vector subspaces of a vector space like $\mathbb{R}^n$ \cite{weisstein_projective_nodate}.
+    we get a definition of projective spaces from one-dimensional vector subspaces of a vector space like $\mathbb{R}^n$ \cite{weisstein_projective_nodate}.
     Here, our dimension comes from a concept of coordinates in the underlying vector space, i.e.\ its basis.
-
     Working purely from axioms we don't have such an obvious idea of dimension.
@@
     \begin{definition}
-        A subspace of the projective space is a subset $X \subseteq P$,
+        A subspace of a projective space $(P, \mathcal{L})$ is a projective space of points $X \subseteq P$ and lines $\mathcal{Y} \subseteq \mathcal{L}$,
         such that any line containing two points of X is a subset of X (that is, completely contained in X).
@@
     \begin{definition}
-        The geometric dimension of the space $P$ is said to be n if that is the largest number for which there is a strictly ascending chain of subspaces of this form:
+        The geometric dimension of the space $(P, \mathcal{L})$ is said to be n if that is the largest number for which there is a strictly ascending chain of subspaces of this form:
+        \begin{center}
             $\emptyset = X_{-1}\subset X_{0}\subset \cdots X_{n}=P.$
+        \end{center}
     \end{definition}
@@
             \centering
-            \begin{tikzpicture}
+            \begin{tikzpicture}[scale=0.7]
                 % Draw the lines

### 2024-11-17 paper/main.tex
Finish proof of theroem 1, try to wrap up future developments section

@@
 \usepackage[T1]{fontenc}
+\usepackage{mathtools}
 
@@
     in which theorems about lines on a projective plane also have duals regarding points (and vice-versa).
-    The second gives rise to a concept of order\cite[p. 24]{beutelspacher_projective_1998}.
+    In finite projective spaces, the second gives rise to a concept of order\cite[p. 24]{beutelspacher_projective_1998}.
 
     \begin{theorem}
-        Given a projective space, there exists a positive integer $q$ such that any line in $L$ contains exactly $q+1$ elements.
+        Given a finite projective space, there exists a positive integer $q$ such that any line in $L$ contains exactly $q+1$ elements.
         We call q the order of this space.
@@
         and thus all lines have the same number of elements.
+        When our set of points is finite, this implies the existence of an integer order.
         If $L_1 = L_2$ we are done, so we consider distinct lines.
 
-        \underline{Case 1}: $L_1$ intersects $L_2$
-
+        \underline{Case 1}: $L_1$ intersects $L_2$.
         Then $\{a, b\} \subseteq L_1$ and $\{a, c\} \subseteq L_2$ for some points $a,b,c$,
         since by A3 both lines contain at least 3 distinct points and by supposition we have at least one shared point.
-
-        As well, by A3 line $bc$ must contain another point, name it $p$, moreover $p \notin L_1, L_2$,
+        By A3 again, line $bc$ must contain another point, name it $p$, moreover $p \notin L_1, L_2$,
         otherwise $L_1 = L_2$ by A1, the uniqueness of lines through points.
@@
         Then given any other point $x \in L_1$, consider the line $xp$.
-        We'll show this must intersect $L_2$ using A2 and call the intersection point $\phi(x)$.
+        We'll show this must intersect $L_2$ and call the intersection point $\phi(x)$.
 
@@
         \end{figure}
+        By A2: If $xa$ intersects $pc$, then $xp$ intersects $ac$.
+        We have $pc=bc$ and $xa = ab$ by A1, so both lines contain $b$ and thus intersect.
+        So $xp$ intersects $ac$.
+        We define the function $\phi(x)$ with domain $L_1$ as follows:
 
-        Given points $a,b,c,d$, if $ab$ intersects $cd$, then $ac$ intersects $bd$
+        \[
+            \phi(x) =
+            \begin{cases}
+                xp \cap L_2 & \text{if } x \neq a \\
+                a & \text{if } x = a
+            \end{cases}
+        \]
 
-        \underline{Case 2}: $L_1$ does not intersect $L_2$
+        Let $x_2\in L_1$ be distinct from $a, x$.
+        Then $\phi(x_2) \neq \phi(x)$,
+        since both pass through p and otherwise by A1 we would have $x = x_2$.
+        Using the same logic as earlier, for $y \in L_2$ distinct from $a$, the line $yp$ intersects $L_1$ at a point $x$ such that $\phi(x)=y$.
+        Finally, since $\phi$ also maps $a \in L_1$ to $a \in L_2$, $\phi$ is a bijection from $L_1$ to $L_2$.
+
+        \underline{Case 2}: $L_1$ does not intersect $L_2$.
+        Let $x \in L_1, y \in L_2$, then the line $L_3 \coloneqq xy$ intersects with both $L_1$ and $L_2$, so from case 1 we have bijections
+        $\phi_1: L_1 \rightarrow L_3$ and $\phi_2: L_3 \rightarrow L_2$, and thus a bijection $\phi_1 \circ \phi_2: L_1 \rightarrow L_3$.
     \end{proof}
@@
     However, finite projective planes are much harder to classify, since they can be constructed in more ways.
-    Specifically, non-Desarguesian planes.
-    The difficulty in classifying finite projective planes gives rise to an open question:
-    \textit{Is the order of a finite projective plane always a prime power?}
-    \todo{Mention examples? State Desargues' theorem?}
+    Specifically, planes that do not satisfy the theorem of Desargues.\cite[\S3]{beutelspacher_projective_1998}
 
+    The difficulty in classifying finite projective planes gives rise to an open conjecture:
+    \textit{The order of a finite projective plane is always a prime power.}
     The number of non-isomorphic finite projective planes is only known up to order 10: $1, 1, 1, 1, 0, 1, 1, 4, 0$
     due to the computational complexity of verifying this using brute force\cite{lam_computer_1991,lam_non-existence_1989}.
-    Moreover, the closest we have come to a proof of this conjecture is the Bruck-Ryser theorem, which states if $n \equiv 1,2\ (mod\ 4)$ and $n$ is not the sum of two squares,
-    then no plane exists of order $n$.
-
-    \todo{Bruck–Ryser theorem}
-    \todo{Classification up to order 10, why is it so difficulty to do past this small number?}
+    The closest we have come to a proof of this conjecture is the Bruck-Ryser theorem\cite[p.~26]{beutelspacher_projective_1998} which states if for positive integer $n$,
+    $n \equiv 1,2\ (mod\ 4)$ and $n$ is not the sum of two squares, then no plane exists of order $n$.
 

### 2024-11-17 src/project.ts
Remove motion canvas, will be generating simple slides instead

@@ -1,8 +1,0 @@
-import {makeProject} from '@motion-canvas/core';
-import audio from '../audio/test.mp3';
-import example from './scenes/example?scene';
-import example2 from "./scenes/example2?scene";
-
-export default makeProject({
-  scenes: [example, example2],
-});

### 2024-11-17 paper/main.tex
Small typo fixes

@@
     It's fairly routine work to show the set of points and lines shown do in fact satisfy our earlier axioms,
-    however more interesting is that this plane has the same number of points and all lines contain three points.
+    however more interesting is that this plane has the same number of points and lines, and all lines contain 3 points.
     Does this generalize to all projective spaces?
@@
     \begin{theorem}
-        Given a finite projective space, there exists a positive integer $q$ such that any line in $L$ contains exactly $q+1$ elements.
-        We call q the order of this space.
+        Given a finite projective space $(P, \mathcal{L})$, there exists a positive integer $q$ such that any line in $\mathcal{L}$ contains exactly $q+1$ elements.
+        We call $q$ the order of this space.
     \end{theorem}
@@
     In fact, when looking at projective geometry through the lens of infinite fields like $\mathbb{R}$,
-    we get a definition of projective spaces from one-dimensional vector subspaces of a vector space like $\mathbb{R}^n$ \cite{weisstein_projective_nodate}.
+    we get a definition of projective spaces from one-dimensional vector subspaces of a vector space like $\mathbb{R}^n$\cite{weisstein_projective_nodate}.
     Here, our dimension comes from a concept of coordinates in the underlying vector space, i.e.\ its basis.
@@
         Finally, the line $xy$ contains points $y,z \in X_2$, and since $X_2$ is a subspace we must have that $xy \in X_2$
-        So, $X_2$ = $P$ since any two points in $P$ form a line (containing them) that is fully contained in $X_2$.
+        So $X_2$ = $P$ since any two points in $P$ form a line (containing them) that is fully contained in $X_2$.
         Thus, the dimension is at most 2.

### 2024-11-18 paper/main.tex
Add marp presentation, fix small typo in bijection phi

@@
         Let $x \in L_1, y \in L_2$, then the line $L_3 \coloneqq xy$ intersects with both $L_1$ and $L_2$, so from case 1 we have bijections
-        $\phi_1: L_1 \rightarrow L_3$ and $\phi_2: L_3 \rightarrow L_2$, and thus a bijection $\phi_1 \circ \phi_2: L_1 \rightarrow L_3$.
+        $\phi_1: L_1 \rightarrow L_3$ and $\phi_2: L_3 \rightarrow L_2$, and thus a bijection $\phi_1 \circ \phi_2: L_1 \rightarrow L_2$.
     \end{proof}
